------------------------------------------------------------------------

------------------------------------------------------------------------

## Revenue Estimate

The table below uses state data to display actual revenue for FY `r fiscal.year - 1` and estimated revenue for FY `r fiscal.year`. Data for the actual revenue column comes from the [Financial Information Database](https://www.mischooldata.org/financial-data-files/) (FID) as well as the the end-of-year August [State Aid Status Report](https://mdoe.state.mi.us/samspublic/Home/StatusReport) (SASR). The FY `r fiscal.year` estimate is produced by updating actual revenue from FY `r fiscal.year - 1` with January SASR data. Additional adjustments are made where payments in the January SASR do not reflect the [state's budget](https://www.legislature.mi.gov/Laws/MCLTablesAndAppropriationActs).


```{r}

No_FID_Avalible <- 
  FA_Data_District %>% 
  filter(FY == fiscal.year - 1) %>% 
  select(fid.r.total) %>% 
  mutate(no.fid.avalible = ifelse(is.na(fid.r.total), 1, 0)) %>% 
  pull()


```

`r if(No_FID_Avalible == 1 ){paste("The Financial Information Database (FID) did not include the data necessary to generate an MEA budget estimate for this district.")}`

```{r}
if(No_FID_Avalible == 0 ){
  
  FA_Data_District %>%
    filter(FY >= (fiscal.year - 1)) %>%
    # select(FY, starts_with("tab."))%>%
    select(FY, tab.rev.local, tab.rev.local.found, tab.rev.local.other, 
           tab.rev.state, starts_with("tab.rev.state"),
           tab.rev.fed, tab.rev.fed.stim, tab.rev.fed.other, tab.rev.other,
           tab.rev.total, tab.rev.net.zero.and.stim, tab.rev.total.xstim.xnet) %>% 
    pivot_longer(cols = c(starts_with("tab.")), 
                 names_to = "Rev_Source", 
                 values_to = "y") %>% 
    mutate(time = ifelse(FY == fiscal.year, "current.year", "last.year" )) %>% 
    pivot_wider(id_cols = Rev_Source, 
                names_from = time, 
                values_from = y) %>% 
    
    # specifying the order of rows
      # mutate(n = row_number(),
      #        n = ifelse(Rev_Source == "tab.rev.total.xstim", 100, n),
      #        n = ifelse(Rev_Source == "tab.rev.total.xstim.xuaal", 101, n)) %>% 
      # arrange(n) %>% 
      # select(-n) %>% 

    mutate(chg = current.year - last.year,
           pct.chg = (chg / last.year) * 100,
           pct.chg = ifelse(is.infinite(pct.chg), NA, pct.chg),
           Rev_Source = 
             case_when(
                        # Local
                        Rev_Source == "tab.rev.local"           ~ "Total Local Revenue",
                        Rev_Source == "tab.rev.local.found"     ~ "Local Foundation Share",
                        Rev_Source == "tab.rev.local.other"     ~ "Local Other",
                        
                        # state
                        Rev_Source == "tab.rev.state"           ~ "Total State Revenue",
                        Rev_Source == "tab.rev.state.found"     ~ "State Foundation Share",
                        Rev_Source == "tab.rev.state.sped"      ~ "Special Education",
                        Rev_Source == "tab.rev.state.31a"       ~ "At-Risk",
                        Rev_Source == "tab.rev.state.41"        ~ "EL / Bilingual",
                        
                        Rev_Source == "tab.rev.state.31aa"      ~ "Mental Health and Safety",
                        Rev_Source == "tab.rev.state.29"        ~ "Enrollment Stabilization",
                        Rev_Source == "tab.rev.state.22l"       ~ "Transportation",
                        Rev_Source == "tab.rev.state.cte"       ~ "CTE / Vocational Education",
                        Rev_Source == "tab.rev.state.edcomp"    ~ "Educator Compensation",

                        
                        Rev_Source == "tab.rev.state.mpsers.uaal" ~ "MPSERS UAAL",
                        Rev_Source == "tab.rev.state.mpsers.netother" ~ "MPSERS Other Net",
                        Rev_Source == "tab.rev.state.mpsers.other"      ~ "MPSERS Other", 
                        
                        Rev_Source == "tab.rev.state.other"     ~ "State Other",
                        
                        # fed 
                        Rev_Source == "tab.rev.fed"             ~ "Total Federal Revenue",
                        Rev_Source == "tab.rev.fed.stim"        ~ "Federal Stimulus",
                        Rev_Source == "tab.rev.fed.other"       ~ "Federal Recurring",
                        
                        # other
                        Rev_Source == "tab.rev.other"           ~ "Other Revenue",
                        Rev_Source == "tab.rev.other.other"     ~ "Other",
                        # Rev_Source == "tab.rev.other.ml.adjustment" ~ "ML Adjustment",
                        
                        # total
                        Rev_Source == "tab.rev.total"           ~ "Total Revenue",
                        Rev_Source == "tab.rev.net.zero.and.stim" ~ "Net Zero and Stimulus",
                        Rev_Source == "tab.rev.total.xstim.xnet" ~ "Total less Stimulus and Net Zero"
                        
                        # Rev_Source == "tab.rev.total.xstim"     ~ "Total less Stimulus",
                        # Rev_Source == "tab.rev.total.xstim.xuaal" ~ "Total less Stimulus and UAAL"


                                  )) %>% 
    
  
    flextable() %>% 
    
    # headers
    set_header_labels(Rev_Source = "",
                      current.year = paste(fiscal.year, "Estimate"),
                       # = paste(fiscal.year, "Estimate"),
  
                      last.year = paste(fiscal.year - 1, "Actual"),
                      chg = "Change",
                      pct.chg = "% Change") %>% 
    
    
    # column formatting 
    colformat_double(j = c("current.year", 
                           "last.year", 
                           "chg"), 
                     big.mark = ",",
                     digits = 0) %>%
  
    colformat_double(j = "pct.chg", suffix = "%") %>% 
    
    
    # bolding section subtotals 
    bold(i = ~ Rev_Source %in% c("Total Local Revenue", 
                               "Total State Revenue",
                               "Total Federal Revenue",
                               "Other Revenue",
                               "Total Revenue"), 
         bold = TRUE, 
         part = "body") %>% 
  
    # horizontal spacing between sections
    padding(i = ~ Rev_Source %in% c(
                               "Total Local Revenue", 
                               "Total State Revenue",
                               "Total Federal Revenue", 
                               "Other Revenue"), padding.top =  15) %>% 
    padding(i = ~ Rev_Source %in% c("Other Revenue"), padding.bottom =  15) %>% 
    
    
    # indentation 
    padding(i = ~ Rev_Source %in% c("Local Foundation Share", 
                                    "Local Other",
                                    
                                    "State Foundation Share", 
                                    "Special Education",
                                    "At-Risk", 
                                    "EL / Bilingual",
                                    "Mental Health and Safety", 
                                    "Enrollment Stabilization",
                                    "Transportation", 
                                    "CTE / Vocational Education",
                                    "Educator Compensation",
                                    "MPSERS UAAL", 
                                    "MPSERS Other Net",
                                    "MPSERS Other", 
                                    "State Other",
                                    
                                    # "Federal Stimulus", "Federal Recurring",
                                    # "Total less Stimulus", "Total less Stimulus and UAAL",
                                    
                                    "Net Zero and Stimulus",
                                    "Total less Stimulus and Net Zero"
                                    ), padding.left = 15) %>% 
    
    
    
    # color coding totals
    bg(i = ~ Rev_Source %in% c("Educator Compensation", 
                               "MPSERS UAAL",
                               "MPSERS Other Net",
                               "Federal Stimulus",
                               "Net Zero and Stimulus"), 
       bg = mea_gray_light,  part = "body") %>% 
    bg(i = ~ Rev_Source == "Total Revenue", bg = mea_blue_light,  part = "body") %>% 
    bg(i = ~ Rev_Source %in% c(
      # "Total less Stimulus and UAAL", 
                               "Total less Stimulus and Net Zero"), 
       bg = mea_green_light,  part = "body") %>% 
    flextable_custom_theme(title = "Table x. Revenue Estimate")
    

}

```

\newpage

```{r}

FA_Data_District %>%
  ungroup() %>%
  mutate(other.net = tab.rev.state.mpsers.netother + tab.rev.state.edcomp) %>% 
  select(FY, tab.rev.total, tab.rev.fed.stim,
         tab.rev.state.mpsers.uaal, other.net, tab.rev.total.xstim.xnet) %>%
  mutate(FY = ifelse(FY == fiscal.year, paste0(FY, " est."), FY)) %>%
  flextable() %>% 
  set_header_labels(FY = "Fiscal Year",
                    tab.rev.total = "Total Revenue",
                    tab.rev.total.xstim.xnet = "Total less Stimulus and Net Zero",
                    tab.rev.fed.stim = "Federal Stimulus",
                    tab.rev.state.mpsers.uaal = "UAAL Payment (147c)",
                    other.net = "Other Net"
                    ) %>%
  colformat_double(j = c("tab.rev.total",
                         "tab.rev.fed.stim", "tab.rev.state.mpsers.uaal"),
                    big.mark = ",", digits = 0) %>%
  bg(j = c("other.net", "tab.rev.fed.stim", "tab.rev.state.mpsers.uaal"), bg = mea_gray_light, part = "all") %>%
  bg(j = "tab.rev.total.xstim.xnet", bg = mea_green_light, part = "all") %>%
  bg(j = "tab.rev.total", bg = mea_blue_light, part = "all") %>%

  flextable_custom_theme(title = "Table x. Revenue Less Stimulus and UAAL")


```

Note: "Revenue Less Stimulus and UAAL" is the preferred measure to fill out MEA's Cost Alignment Calculator (CAC). These dollars represent revenues that are not one-time federal stimulus nor 147c payments that must by law be submitted to the Office of Retirement Services (ORS).

```{r}

FA_Data_District %>%
  select(FY, tab.rev.total, tab.rev.total.xstim.xnet) %>%
  pivot_longer(cols = c(tab.rev.total, tab.rev.total.xstim.xnet)) %>%
  filter(!is.na(value)) %>%
  mutate(name = case_when(name == "tab.rev.total"  ~ "Total Revenue",
                            name == "tab.rev.total.xstim.xnet" ~ "Revenue less Stimuls and Net")) %>%

  ggplot(aes(x = FY, y = value,
             group = name,  color = name, linetype = name))+
  geom_rect(xmin = fiscal.year - 1, xmax = fiscal.year,
            ymin = -Inf,
            ymax = max(FA_Data_District$tab.rev.total) * 1.025, color = NA,
            fill = mea_gray_light)+
  coord_cartesian(clip = 'off')+
  annotate("text",
         label = "Estimate",
         x = fiscal.year - 0.5,
         y = max(FA_Data_District$tab.rev.total) * 1.05,
         alpha = .75) +
  geom_line(size = line_size, fill = NA) +
  expand_limits(x = fiscal.year + 0.5  )+
  scale_x_continuous(breaks = seq(1990, 2100, by = 1) )+
  scale_y_continuous(labels = number_format(big.mark = ",")) +
  labs(title = "Figure x. <span style='color: #003057'> Total Revenue</span> and <span style='color: #00A651'> Revenue less Stimuls and UAAL</span>",
       x = "Fiscal Year",
       y = "")+
  scale_color_manual(values = c(mea_green, mea_blue)) +
  scale_fill_manual(values = c(mea_green, mea_blue)) +
  scale_linetype_manual(values=c("solid", "twodash"))+
  theme(legend.box.background = element_rect(color= mea_gray, size=1),
        legend.title = element_blank(),
        legend.position = "bottom",
        plot.title = element_markdown())

```
