---
param:
  district: 1010
editor_options: 
  markdown: 
    wrap: 72
---




## Transfers

```{r}
district_fb_transfer_data <- 
  FA_Data_District %>% 
  fa_helper_fa_data_to_transfer_data() %>% 
  ungroup()


transfer_back_calc <- 
  district_fb_transfer_data %>% 
  filter(FY != fiscal.year) %>% 
  filter(fund %in% funds_to_include) %>% 
  arrange(fund, FY) %>%  
  select(FY, fund, fund.name.trans.to, fb.total,transfered.from.gf) %>%  
  group_by(fund) %>%
  mutate(transfer.cumulative = cumsum(transfered.from.gf),
         transfer.back.possible = accumulate2(.x = transfered.from.gf[-1],
                          .y = fb.total[-1],
                          .f = ~ min(.x + ..2, ..3),
                          .init = transfered.from.gf[1]),
         transfer.back.possible = ifelse(transfer.back.possible < 0 , 0, transfer.back.possible)

  ) %>% 
  filter(max(transfer.cumulative) > 0)


```



```{r, include = FALSE, message = FALSE}
non_restricted_balance <- 
  district_fb_transfer_data %>% 
  filter(FY == fiscal.year - 1,
         fund %in% funds_to_include) %>% 
  ungroup() %>% 
  summarise(amount = sum(fund.balance.unrestricted, na.rm = TRUE)) %>% 
  pull()


total_transfered_out_in_10_years <- 
  district_fb_transfer_data %>% 
  ungroup() %>% 
  filter(fund %in% funds_to_include,
         transfered.from.gf != 0,
         FY >= fiscal.year - 11) %>% 
  summarise(amount = sum(transfered.from.gf, na.rm = TRUE)) %>% 
  pull()


total_amount_to_transfer_back <- 
  transfer_back_calc %>% 
  ungroup() %>% 
  filter(FY == fiscal.year - 1) %>% 
  summarise(transfer.back.possible = sum(transfer.back.possible, na.rm = TRUE)) %>% 
  pull()


# this is the easy but wrong way to do it
# total_amount_to_transfer_back <- 
#   if(total_transfered_out_in_10_years > non_restricted_balance) {
#   non_restricted_balance
#     } else {total_transfered_out_in_10_years}




new_gf_bal <- var_to_words(fid.b.fb.11) + total_amount_to_transfer_back

new_gf_bal_pct_rev <- new_gf_bal / var_to_words(fid.r.total.audit)

new_gf_bal_pct_exp <- new_gf_bal / var_to_words(fid.e.total.xtrans)




```

Dollars transferred out of the General Fund are not recorded in the General Fund balance. While many interfund transfers are routine and benign, large transfers out of the General Fund can make the district appear artificially worse off financially. Table xx lists each transfer out of the General Fund. Note, some transfers, including those to the food service fund, cannot be transferred back to the General Fund.  


```{r}

dist_gf_rev <-
  FA_Data_District %>%
  select(FY, fid.r.total.audit)

# add percent of GF revenue from that year. 
district_fb_transfer_data %>% 
  filter(fund != 11,
    # fund %in% funds_to_include,
         transfered.from.gf != 0,
         FY >= fiscal.year - 11) %>% 
  ungroup() %>% 
  select(FY, fund.name.trans.to, transfered.from.gf) %>% 
  group_by(FY) %>% 
  group_modify(~.x %>%   adorn_totals(where = "row", name = "Subtotal")) %>% 
  left_join(dist_gf_rev, by = "FY") %>% 
  mutate(pct.of.gf.rev = (transfered.from.gf / fid.r.total.audit) * 100) %>% 
  select(-fid.r.total.audit) %>% 
  flextable() %>% 
  hline(i = ~ fund.name.trans.to == "Subtotal", border = fp_border_default()) %>% 
  bold(i = ~ fund.name.trans.to == "Subtotal", bold = TRUE) %>%
  set_header_labels(fund.name.trans.to = "Fund",
                    transfered.from.gf = "Amount",
                    pct.of.gf.rev = "% of General Fund Revenue") %>% 
  colformat_num(j = "FY", big.mark = "") %>%
  colformat_double(j = "pct.of.gf.rev", suffix = "%", digits = 2) %>% 
  colformat_double(j = c("transfered.from.gf"), big.mark = ",", digits = 0) %>%
  flextable_custom_theme(title = "Table x. Transfers Out of the General Fund")


```


```{r, fig.height = 2.5, eval=FALSE}
district_fb_transfer_data %>% 
  filter(FY <= fiscal.year - 1) %>% 
  group_by(FY) %>% 
  summarise(value = sum(transfered.from.gf, na.rm = TRUE)) %>% 
  ggplot(aes(FY, value)) +
  geom_col() +
  scale_x_continuous(breaks = seq(1990, 2100, by = 1))+
  scale_y_continuous(labels = comma_format(), 
                     # limits = c(0, max_fb)
                     )+
  labs(title = "Figure x. Total Transfers out of the General Fund Balance",
       x = "Fiscal Year",
       y = "")


```





In `r var_to_words(FY)`, `r var_to_words(district.label)` had a general
fund balance of `r var_to_words(fid.b.fb.11) %>% currency(digits = 0)`.
That equates to
`r (var_to_words(fid.b.fb.11.pct.rev) / 100) %>% percent()` of total
revenue and `r (var_to_words(fid.b.fb.11.pct.exp) / 100) %>% percent()`
of total expenditure. In the last 10 years,
`r total_transfered_out_in_10_years %>% currency(digits = 0)` was
transferred out of the General Fund. 
As reported in their `r var_to_words(FY)` state financial data,
`r var_to_words(district.label)` maintained
`r non_restricted_balance %>% currency(digits = 0)` of
non-restricted resources (i.e., committed, assigned, or unassigned) outside of the General Fund. Up to `r total_amount_to_transfer_back %>% currency(digits = 0)` dollars may be eligible to be transferred back to the General Fund. If these resources were transferred back to the General Fund, it would total
`r new_gf_bal %>% currency(digits = 0)`--which would equate to
`r new_gf_bal_pct_rev %>% percent()` of revenue and
`r new_gf_bal_pct_exp %>% percent()` of expenditure respectively. 


```{r}

transfer_back_calc %>% 
  ungroup() %>% 
  filter(FY == fiscal.year - 1) %>% 
  select(fund.name.trans.to, transfer.back.possible) %>% 
  adorn_totals() %>% 
  flextable() %>% 

  set_header_labels(fund.name.trans.to = "Fund",
                    transfer.back.possible = "GF transfer back calculation") %>% 
  colformat_double(j = c("transfer.back.possible"), big.mark = ",", digits = 0) %>% 
  bold(i = ~fund.name.trans.to == "Total") %>% 
  flextable_custom_theme(title =  paste0("Table x. Estimated Amount to Transfer Back to General Fund, FY ", 
                                    fiscal.year-1))

```

The following table shows the iterative calculation by fund used to estimate the total assets eligible to be transfered back to the General Fund. The calculation assumes that resources transferred out of the General Fund can be transferred back unless the receiving fund balance falls below the cumulative transfer in. 

```{r}

transfer_back_calc %>% 
  ungroup() %>% 
  select(FY, fund.name.trans.to, transfered.from.gf, fb.total, transfer.back.possible) %>% 
  flextable() %>% 
  set_header_labels(FY = "Fiscal Year",
                    fund.name.trans.to = "Fund",
                    transfered.from.gf = "Amount transfered from GF",
                    fb.total = "Fund blance total",
                    transfer.back.possible = "GF transfer back calculation") %>% 

  colformat_double(big.mark = ",",
                   digits = 0) %>% 
  colformat_num(j = "FY",
                big.mark = "") %>% 
  flextable_custom_theme(title = "Table x. Transfers Back to General Fund Calculation")
  



```



