```{r}

prior.years.to.show <- 9

```

## Budget Comparison

The following table and figure is intended to help asses the accuracy of the **current MEA revenue estimate** (as detailed in the "Revenue Estimate" section). Consequently, the table and figure below do not show the MEA revenue estimated in that year. Rather, they apply the current mechanical model used to estimate revenue to historical data. For comparison, the table and figure also include the **actual revenue** (received by the district's General Fund), the district's **original budget** (showing their revenue estimate as of July), and the **baseline** (which assumes no change in revenue from the previous fiscal year). 



```{r}



FA_Data_District %>% 
  
    select(FY, fid.r.total.audit, 
         db.original.total.revenue, fid.r.total.audit.lag1, est.1.rev.total,
         db.orig.rev.pct.act, fid.r.total.audit.lag1.pct.act, est.1.rev.total.pct.act) %>% 

  filter(FY > (fiscal.year - prior.years.to.show)) %>% 
  flextable() %>% 
  set_header_labels(FY = "Fiscal Year",
                    fid.r.total.audit = "Actual Revenue",
                    db.original.total.revenue = "District Original Budget",
                    fid.r.total.audit.lag1 = "Baseline Revenue",
                    est.1.rev.total = "Current MEA Revenue Estimate",
                    db.orig.rev.pct.act = "Original Budget % of Actual",
                    fid.r.total.audit.lag1.pct.act = "Baseline % of Actual",
                    est.1.rev.total.pct.act = "Current MEA Estimate % of Actual") %>%
  colformat_num(j = "FY", big.mark = "") %>%
  colformat_num(j = c("fid.r.total.audit", 
                      "fid.r.total.audit.lag1",
                      "db.original.total.revenue", 
                      "est.1.rev.total"), big.mark = ",")%>%
  colformat_double(j = c("db.orig.rev.pct.act",
                         "fid.r.total.audit.lag1.pct.act",
                         "est.1.rev.total.pct.act"), suffix = "%") %>% 
  # flextable::footnote(i = 1, j = "fid.r.total.audit.lag1", 
  #          value = as_paragraph("This column 'estimates' revenue in  the current year by using the prior year's actual total revenue."),
  #          ref_symbols = c("1"), 
  #          part = "header") %>% 
  # flextable::footnote(i = 1, j = "est.1.rev.total", 
  #          value = as_paragraph("MEA revenue estimate includes federal stimulus."),
  #          ref_symbols = c("2"), 
  #          part = "header") %>% 
  
  bg(j = "db.orig.rev.pct.act", bg = mea_blue_light, part = "all") %>% 
  bg(j = "fid.r.total.audit.lag1.pct.act", bg = mea_gray_light, part = "all") %>%
  bg(j = "est.1.rev.total.pct.act", bg = mea_red_light, part = "all") %>% 


  flextable_custom_theme()


```

```{r, fig.height = 3.5}

district_budget_data <- 
  FA_Data_District %>% 
  filter(FY > (fiscal.year - prior.years.to.show),
         !is.na(est.1.rev.total.pct.act)) %>% 
  select(FY, db.orig.rev.pct.act, 
         fid.r.total.audit.lag1.pct.act, 
         est.1.rev.total.pct.act) %>% 
  pivot_longer(cols = c(db.orig.rev.pct.act, 
                        fid.r.total.audit.lag1.pct.act, 
                        est.1.rev.total.pct.act))


district_budget_min <- 
  district_budget_data %>% 
  filter(!is.na(value)) %>% 
  summarise(min = min(value) / 100) %>% 
  pull()

district_budget_max <- 
  district_budget_data %>% 
  filter(!is.na(value)) %>% 
  summarise(max = max(value) / 100) %>% 
  pull()


district_budget_data %>% 
  # mutate(label = case_when(FY == max(FY) & name == "db.orig.rev.pct.act"            ~ "Original Budget",
  #                          FY == max(FY) & name == "fid.r.total.audit.lag1.pct.act" ~ "  Prior Year        ",
  #                          FY == max(FY) & name == "est.1.rev.total.pct.act"        ~  "MEA Estimate "),


  mutate(name = case_when( name == "db.orig.rev.pct.act"            ~ "Original Budget",
                           name == "fid.r.total.audit.lag1.pct.act" ~ "  Baseline        ",
                            name == "est.1.rev.total.pct.act"        ~  "MEA Estimate "),
                  value = value / 100) %>% 
  
  ggplot(aes(x = FY, y = value, 
             group = name, 
             # label = label, 
             color = name, 
             linetype = name), 
         size = line_size)+
  geom_line(size = line_size) +
  geom_hline(yintercept = 1, size = line_size, alpha = .5) +
  expand_limits(x = fiscal.year)+
  
    # geom_text_repel(aes(label = label, 
    #                    color = name
    #                    ),
    #                 box.padding = .5,
    #                 # point.padding = 10,
    #                 
    #                 min.segment.length = .2,
    #               # nudge_x = 1.4,
    #               na.rm = TRUE)+
  
  annotate("rect", xmin = 2021, xmax = 2024,
           ymin = district_budget_min,
           ymax = district_budget_max * 1.015,
           alpha = .15) +
  annotate("text", 
           label = "ESSER Period",
           x = 2022.5,
           y = district_budget_max * 1.005,
           alpha = .75) +
  
  scale_x_continuous(breaks = seq(1990, 2100, by = 1) )+
  scale_y_continuous(labels = percent_format(), expand = c(0, 0)) +
  
  labs(title = 
"<b>District's <span style='color: #003057'> Original Budget</span></b> , <b><span style='color:#00A651 '>Baseline</span></b> , and
<b><span style='color:#C2002F '> MEA Estimate </span></b> 
as Percent of Actual Revenue",
       x = "Fiscal Year",
       y = "",
legend = "")+
  scale_color_manual(values = c(mea_green, mea_red, mea_blue)) +
  scale_fill_manual(values = c(mea_green, mea_red, mea_blue)) +
  scale_linetype_manual(values=c("twodash", "solid", "dotted"))+
  theme(
    # legend.position = c(.95, .95),
    # legend.justification = c("right", "top"),
    legend.box.just = "right",
    # legend.margin = margin(6, 6, 6, 6),
    legend.box.background = element_rect(color= mea_gray, size=1),
    legend.title = element_blank(),
    legend.position = "bottom",
    plot.title = element_markdown()) 


```

\newpage

The following table and figure compares the surplus or deficit expected by the district in their original budget  to the actual surplus or deficit. A **surplus** occurs revenue is greater than expenditure within a fiscal year. A **deficit** occurs revenue is lesser than expenditure within a fiscal year. 


```{r}
prior.years.to.show <- 9
```


```{r}


FA_Data_District %>%
  ungroup() %>% 
  filter(FY != fiscal.year) %>% 
  select(FY, db.orig.surplus.deficit, fid.surplus.deficit, db.orig.surplus.error) %>%
  flextable() %>%
  add_header_lines(values = "Surplus/Deficit") %>% 

  set_header_labels(FY = "Fiscal Year",
                    fid.surplus.deficit = "Actual",
                    db.orig.surplus.deficit = "Original Budget",
                    db.orig.surplus.error = "Original Budget Error (Budget - Actual)") %>%
  colformat_num(j = "FY",
                big.mark = "") %>%
  colformat_double(j = c("fid.surplus.deficit",
                         "db.orig.surplus.deficit"),
                   big.mark = ",",
                   digits = 0) %>%
  
  # Option #1. this code does a light shade for the two columns.
  bg(j = "fid.surplus.deficit", bg = mea_blue_light, part = "all") %>%
  bg(j = "db.orig.surplus.deficit", bg = mea_red_light, part = "all") %>%
  
  
  # option #2. dark shade on the header. Decided to keep it the same
      # bg(j = "fid.surplus.deficit", bg = mea_blue, part = "header") %>%
      # color(j = "fid.surplus.deficit",
      #       color = "white", part = "header") %>%
      # 
      # bg(j = "db.orig.surplus.deficit", bg = mea_red, part = "header") %>%
      # color(j = "db.orig.surplus.deficit",
      #       color = "white", part = "header") %>%

  flextable_custom_theme()




```


```{r eval = FALSE}

# old version of figure no longer in use
FA_Data_District %>%
  ggplot(aes(x = FY)) +
  geom_col(aes(y = fid.surplus.deficit), 
           fill = mea_blue,
           width = .25,
           just = 0)+
  geom_col(aes(y = db.orig.surplus.deficit),
           fill = mea_red,
           width = .25,
           just = 1) +
  geom_hline(yintercept = 0)+
  scale_x_continuous(breaks = seq(1990, 2100, by = 1) )+
  scale_y_continuous(labels = number_format(big.mark = ",")) +
  labs(title = "<span style='color: #C2002F '> Original Budget</span> and <span style='color: #003057'> Actual</span> Surplus/Deficit",
       x = "Fiscal Year",
       y = "") +
  theme(
    plot.title = element_markdown()
  )

```


```{r }

FA_Data_District %>%
  filter(FY != fiscal.year,
        !is.na(fid.surplus.deficit) & !is.na(db.orig.surplus.deficit)) %>% 
  ggplot(aes(x = FY)) +
  geom_hline(yintercept = 0)+
  geom_segment(aes(xend = FY, y = fid.surplus.deficit, yend = db.orig.surplus.deficit)) +
  geom_point(aes(y = fid.surplus.deficit, 
                 color = "Actual",
                 shape = "Actual"), 
             size = 3, alpha = 1)+
  geom_point(aes(y = db.orig.surplus.deficit, 
                 color = "Original Budget",
                 shape = "Original Budget"),
           # color = mea_red, 
           size = 3, alpha = 1) +
  
  scale_x_continuous(breaks = seq(1990, 2100, by = 1) )+
  scale_y_continuous(labels = number_format(big.mark = ",")) +
  labs(title = "Surplus/Deficit",
       subtitle = "<span style='color: #C2002F '> Original Budget</span> vs. <span style='color: #003057'>Actual</span>",
       x = "Fiscal Year",
       y = "") +
  scale_color_manual(name = "", values = c("Original Budget" = mea_red, "Actual" = mea_blue))+
  scale_shape_manual(name = "", values = c("Original Budget" = "circle", "Actual" = "square")) +
  theme(
    plot.subtitle = element_markdown(),
    legend.box.background = element_rect(color= mea_gray, size=1),
        legend.position = "bottom"  )



```




\newpage

The following two tables compare General Fund revenue and expenditure expected in the district's original budget to the actual revenue earned and expenditure spent in that fiscal year. 

```{r}
FA_Data_District %>% 
  filter(FY > (fiscal.year - prior.years.to.show),
         !is.na(est.1.rev.total.pct.act)) %>% 
  select(FY, db.original.total.revenue, fid.r.total.audit, db.orig.rev.error) %>% 
  flextable() %>%
  add_header_lines(values = "General Fund Revenue") %>% 
  set_header_labels(
                  FY = "Fiscal Year",
                  fid.r.total.audit = "Actual",
                  db.original.total.revenue = "Original Budget",
                  db.orig.rev.error = "Original Budget Error (Budget - Actual)") %>% 
  colformat_num(j = "FY", big.mark = "") %>%
  colformat_double(j = c("fid.r.total.audit",
                      "db.original.total.revenue", 
                      "db.orig.rev.error"), 
                big.mark = ",",
                digits = 0) %>%
  flextable_custom_theme()

```


```{r}


FA_Data_District %>% 
  filter(FY > (fiscal.year - prior.years.to.show),
         !is.na(est.1.rev.total.pct.act)) %>% 
  select(FY, db.original.total.expenditure, fid.e.total.xtrans, db.orig.exp.error) %>% 
  flextable() %>% 
  add_header_lines(values = "General Fund Expenditure") %>% 
  set_header_labels(
                  FY = "Fiscal Year",
                  fid.e.total.xtrans = "Actual",
                  db.original.total.expenditure = "Original Budget",
                  db.orig.exp.error = "Original Budget Error (Budget - Actual)") %>% 
  colformat_num(j = "FY", big.mark = "") %>%
  colformat_double(j = c("fid.e.total.xtrans",
                      "db.original.total.expenditure", 
                      "db.orig.exp.error"), 
                big.mark = ",",
                digits = 0) %>%
  flextable_custom_theme()



```
