---
param:
  district: 1010
editor_options: 
  markdown: 
    wrap: 72
---

## Transfers

```{r}
district_fb_transfer_data <- 
  FA_Data_District %>% 
  fa_helper_fa_data_to_transfer_data() %>% 
  ungroup()

funds_to_include <- c(21, 22, 23, 24, 26, 27, 28, 29, seq(40, 49))
```

```{r}

var_to_words <- function(var) {
  
  FA_Data_District %>% 
    filter(FY == max(FY) - 1) %>% 
    select({{ var }}) %>% 
    unique() %>% 
    pull()
  
}

```

```{r, include = FALSE, message = FALSE}
total_amount_to_transfer_back <- 
  district_fb_transfer_data %>% 
  filter(FY == fiscal.year - 1,
         fund %in% funds_to_include) %>% 
  ungroup() %>% 
  summarise(amount = sum(fund.balance.unrestricted, na.rm = TRUE)) %>% 
  pull()


total_transfered_out_in_5_years <- 
  district_fb_transfer_data %>% 
  ungroup() %>% 
  filter(fund %in% funds_to_include,
         transfered.from.gf != 0,
         FY >= fiscal.year - 5) %>% 
  summarise(amount = sum(transfered.from.gf, na.rm = TRUE)) %>% 
  pull()


new_gf_bal <- var_to_words(fid.b.fb11) + total_amount_to_transfer_back

new_gf_bal_pct_rev <- new_gf_bal / var_to_words(fid.r.total.audit)

new_gf_bal_pct_exp <- new_gf_bal / var_to_words(fid.e.total.xtrans)



```

In `r var_to_words(FY)`, `r var_to_words(district.label)` had a general
fund balance of `r var_to_words(fid.b.fb11) %>% currency(digits = 0)`.
That equates to
`r (var_to_words(fid.b.fb.11.pct.rev) / 100) %>% percent()` of total
revenue and `r (var_to_words(fid.b.fb.11.pct.exp) / 100) %>% percent()`
of total expenditure. In the last 5 years,
`r total_transfered_out_in_5_years %>% currency(digits = 0)` was
transferred out of the General Fund. As of `r var_to_words(FY)`,
`r var_to_words(district.label)` maintained
`r total_amount_to_transfer_back %>% currency(digits = 0)` of
unrestricted resources outside of the General Fund. These dollars can
be transferred to the General Fund. If these funds were transferred to
the General Fund, it would total
`r new_gf_bal %>% currency(digits = 0)`--which would equate to
`r new_gf_bal_pct_rev %>% percent()` of revenue and
`r new_gf_bal_pct_exp %>% percent()` of expenditure respectively.

```{r}

district_fb_transfer_data %>% 
  filter(FY == fiscal.year - 1,
         !is.na(fund.balance.unrestricted),
         fund.balance.unrestricted != 0,
         fund %in% funds_to_include) %>% 
  ungroup() %>% 
  select(fund.name.trans.to, fund.balance.unrestricted) %>% 

  janitor::adorn_totals(name = 'Total') %>% 

  flextable() %>% 
  add_header_lines(values = "Current Fund Balance Avalible to Transfer Back to the General Fund") %>% 
  set_header_labels(fund.balance.unrestricted = "Unrestricted Fund Balance",
                    fund.name.trans.to = "Fund") %>% 
  flextable_custom_theme()

```

\newline


```{r}

district_fb_transfer_data %>% 
  filter(fund %in% funds_to_include,
         transfered.from.gf != 0,
         FY >= fiscal.year - 10) %>% 
  ungroup() %>% 
  select(FY, fund.name.trans.to, transfered.from.gf) %>% 
  flextable() %>% 
  add_header_lines(values = "Transfers Out of the General Fund") %>% 
  set_header_labels(fund.name.trans.to = "Fund",
                    transfered.from.gf = "Amount") %>% 
  colformat_num(j = "FY", big.mark = "") %>%
  colformat_double(j = c("transfered.from.gf"), big.mark = ",", )%>%
  flextable_custom_theme()


```




