```{r}

prior.years.to.show <- 12

```

## Budget Comparison




```{r, eval = FALSE}



FA_Data_District %>% 
  
    select(FY, fid.r.total.audit, 
         db.original.total.revenue, fid.r.total.audit.lag1, est.1.rev.total,
         db.orig.rev.pct.act, fid.r.total.audit.lag1.pct.act, est.1.rev.total.pct.act) %>% 

  filter(FY > (fiscal.year - prior.years.to.show)) %>% 
  flextable() %>% 
  set_header_labels(FY = "Fiscal Year",
                    fid.r.total.audit = "Actual Revenue",
                    db.original.total.revenue = "District Original Budget",
                    fid.r.total.audit.lag1 = "Baseline Revenue",
                    est.1.rev.total = "Current MEA Revenue Estimate",
                    db.orig.rev.pct.act = "Original Budget % of Actual",
                    fid.r.total.audit.lag1.pct.act = "Baseline % of Actual",
                    est.1.rev.total.pct.act = "Current MEA Estimate % of Actual") %>%
  colformat_num(j = "FY", big.mark = "") %>%
  colformat_num(j = c("fid.r.total.audit", 
                      "fid.r.total.audit.lag1",
                      "db.original.total.revenue", 
                      "est.1.rev.total"), big.mark = ",")%>%
  colformat_double(j = c("db.orig.rev.pct.act",
                         "fid.r.total.audit.lag1.pct.act",
                         "est.1.rev.total.pct.act"), suffix = "%") %>% 
  # flextable::footnote(i = 1, j = "fid.r.total.audit.lag1", 
  #          value = as_paragraph("This column 'estimates' revenue in  the current year by using the prior year's actual total revenue."),
  #          ref_symbols = c("1"), 
  #          part = "header") %>% 
  # flextable::footnote(i = 1, j = "est.1.rev.total", 
  #          value = as_paragraph("MEA revenue estimate includes federal stimulus."),
  #          ref_symbols = c("2"), 
  #          part = "header") %>% 
  
  bg(j = "db.orig.rev.pct.act", bg = mea_blue_light, part = "all") %>% 
  bg(j = "fid.r.total.audit.lag1.pct.act", bg = mea_green_light, part = "all") %>%
  bg(j = "est.1.rev.total.pct.act", bg = mea_red_light, part = "all") %>% 


  flextable_custom_theme(title = "Table x. Revenue Estimate Comparison")


```

```{r, fig.height = 3.5, eval = FALSE}

district_budget_data <- 
  FA_Data_District %>% 
  filter(FY > (fiscal.year - prior.years.to.show),
         !is.na(est.1.rev.total.pct.act)) %>% 
  select(FY, db.orig.rev.pct.act, 
         fid.r.total.audit.lag1.pct.act, 
         est.1.rev.total.pct.act) %>% 
  pivot_longer(cols = c(db.orig.rev.pct.act, 
                        fid.r.total.audit.lag1.pct.act, 
                        est.1.rev.total.pct.act))


district_budget_min <- 
  district_budget_data %>% 
  filter(!is.na(value)) %>% 
  summarise(min = min(value) / 100) %>% 
  pull()

district_budget_max <- 
  district_budget_data %>% 
  filter(!is.na(value)) %>% 
  summarise(max = max(value) / 100) %>% 
  pull()


district_budget_data %>% 
  # mutate(label = case_when(FY == max(FY) & name == "db.orig.rev.pct.act"            ~ "Original Budget",
  #                          FY == max(FY) & name == "fid.r.total.audit.lag1.pct.act" ~ "  Prior Year        ",
  #                          FY == max(FY) & name == "est.1.rev.total.pct.act"        ~  "MEA Estimate "),


  mutate(name = case_when( name == "db.orig.rev.pct.act"            ~ "Original Budget",
                           name == "fid.r.total.audit.lag1.pct.act" ~ "  Baseline        ",
                            name == "est.1.rev.total.pct.act"        ~  "MEA Estimate "),
                  value = value / 100) %>% 
  
  ggplot(aes(x = FY, y = value, 
             group = name, 
             # label = label, 
             color = name, 
             linetype = name), 
         size = line_size)+
    annotate("rect", xmin = 2021, xmax = 2024,
           ymin = district_budget_min,
           ymax = district_budget_max * 1.015,
           fill = mea_gray_light) +
  annotate("text", 
           label = "ESSER Period",
           x = 2022.5,
           y = district_budget_max * 1.005,
           alpha = .75) +
  geom_line(size = line_size) +
  geom_hline(yintercept = 1, size = line_size, alpha = .5) +
  expand_limits(x = fiscal.year)+
  
    # geom_text_repel(aes(label = label, 
    #                    color = name
    #                    ),
    #                 box.padding = .5,
    #                 # point.padding = 10,
    #                 
    #                 min.segment.length = .2,
    #               # nudge_x = 1.4,
    #               na.rm = TRUE)+
  

  
  scale_x_continuous(breaks = seq(1990, 2100, by = 1) )+
  scale_y_continuous(labels = percent_format(), expand = c(0, 0)) +
  
  labs(title = 
"<b>District's <span style='color: #003057'> Original Budget</span></b> , <b><span style='color:#00A651 '>Baseline</span></b> , and
<b><span style='color:#C2002F '> MEA Estimate </span></b> 
as Percent of Actual Revenue",
       x = "Fiscal Year",
       y = "",
legend = "")+
  scale_color_manual(values = c(mea_green, mea_red, mea_blue)) +
  scale_fill_manual(values = c(mea_green, mea_red, mea_blue)) +
  scale_linetype_manual(values=c("twodash", "solid", "dotted"))+
  theme(
    # legend.position = c(.95, .95),
    # legend.justification = c("right", "top"),
    legend.box.just = "right",
    # legend.margin = margin(6, 6, 6, 6),
    legend.box.background = element_rect(color= mea_gray, size=1),
    legend.title = element_blank(),
    legend.position = "bottom",
    plot.title = element_markdown()) 


```

Table 3 and figure 2 compares the surplus or deficit expected by the district in their original and final budgets  to the actual surplus or deficit. A **surplus** occurs when revenue is greater than expenditure within a fiscal year. A **deficit** occurs when revenue is less than expenditure within a fiscal year. 



```{r}


FA_Data_District %>%
  ungroup() %>% 
  filter(FY != fiscal.year) %>% 
  # mutate(db.orig.surplus.deficit.pct.error = (db.orig.surplus.error / fid.surplus.deficit) * 100,
  #        db.final.surplus.deficit.pct.error = (db.final.surplus.error / fid.surplus.deficit)* 100) %>% 
  select(FY, fid.surplus.deficit, 
         db.orig.surplus.deficit,  db.orig.surplus.error,
         db.final.surplus.deficit, db.final.surplus.error) %>% 
  flextable() %>%
    add_header_row(values = c("", "Original Budget", "Final Budget"),
                 colwidths = c(2,2,2)) %>% 
  set_header_labels(FY = "Fiscal Year",
                    fid.surplus.deficit = "Actual",
                    db.orig.surplus.deficit = "Amount",
                    db.orig.surplus.error = "Budget Error",
                    # db.orig.surplus.deficit.pct.error = "% Error",
                    
                    db.final.surplus.deficit = "Amount",
                    db.final.surplus.error = "Budget Error"
                    # db.final.surplus.deficit.pct.error = "% Error"
                    ) %>%
  colformat_num(j = "FY",
                big.mark = "") %>%
  colformat_double(j = c("fid.surplus.deficit",
                         "db.orig.surplus.deficit",
                         "db.orig.surplus.error", 
                         "db.final.surplus.deficit",
                         "db.final.surplus.error"),
                   big.mark = ",",
                   digits = 0) %>%
  # colformat_double(j = c("db.orig.surplus.deficit.pct.error", 
  #                        "db.final.surplus.deficit.pct.error"), suffix = "%") %>% 
  bg(j = "fid.surplus.deficit", bg = mea_gray_light, part = "all") %>%
  bg(j = c("db.orig.surplus.deficit", 
           "db.orig.surplus.error"), bg = mea_red_light, part = "all") %>% 
    bg(j = c("db.final.surplus.deficit", 
             "db.final.surplus.error"), bg = mea_blue_light, part = "all") %>% 
  flextable_custom_theme(title = "Table 3. Surplus/Deficit, Original Budget and Actual")


```




```{r }

FA_Data_District %>%
  filter(FY != fiscal.year,
        !is.na(fid.surplus.deficit) & !is.na(db.orig.surplus.deficit)) %>% 
  ggplot(aes(x = FY)) +
  geom_hline(yintercept = 0)+
  geom_segment(aes(xend = FY, y = fid.surplus.deficit, yend = db.orig.surplus.deficit)) +
  geom_point(aes(y = fid.surplus.deficit, 
                 color = "Actual",
                 shape = "Actual"), 
             size = 3, alpha = 1)+
  geom_point(aes(y = db.orig.surplus.deficit, 
                 color = "Original Budget",
                 shape = "Original Budget"),
           # color = mea_red, 
           size = 3, alpha = 1) +
    geom_point(aes(y = db.final.surplus.deficit, 
                 color = "Final Budget",
                 shape = "Final Budget"),
           # color = mea_red, 
           size = 3, alpha = 1) +
  scale_x_continuous(breaks = seq(1990, 2100, by = 1) )+
  scale_y_continuous(labels = number_format(big.mark = ",")) +
  labs(title = "Figure 2. Surplus/Deficit",
       # subtitle = "<span style='color: #C2002F '> Original Budget</span> vs. <span style='color: #3F3F3F'>Actual</span>",
       x = "Fiscal Year",
       y = "") +
  scale_color_manual(name = "", values = c("Original Budget" = mea_red, "Actual" = mea_gray, "Final Budget" = mea_blue))+
  scale_shape_manual(name = "", values = c("Original Budget" = "circle", "Actual" = "square", "Final Budget" = "diamond")) +
  theme(
    plot.subtitle = element_markdown(),
    legend.box.background = element_rect(color= mea_gray, size=1),
        legend.position = "bottom"  )



```


### Budgeted Revenue

Table 4 and figure 3 compare General Fund revenue expected in the district's original and final budgets to the actual revenue earned in that fiscal year. 

```{r}
FA_Data_District %>% 
  filter(FY > (fiscal.year - prior.years.to.show),
         FY < fiscal.year
         ) %>% 
  select(FY, fid.r.total.audit ,
         db.original.total.revenue, db.orig.rev.error, db.orig.rev.pct.act,
         db.final.total.revenue, db.final.rev.error, db.final.rev.pct.act) %>% 
  flextable() %>%
  add_header_row(values = c("", "Original Budget", "Final Budget"),
                 colwidths = c(2,3,3)) %>% 
  set_header_labels(
                  FY = "Fiscal Year",
                  fid.r.total.audit = "Actual",
                  
                  db.original.total.revenue = "Amount",
                  db.orig.rev.error = "Budget Error",
                  db.orig.rev.pct.act = "% of Actual ", 
                  
                  db.final.total.revenue = "Amount",
                  db.final.rev.error = "Budget Error",
                  db.final.rev.pct.act = "% of Actual") %>% 
  colformat_double(big.mark = ",", digits = 0) %>%
  colformat_num(j = "FY", big.mark = "") %>% 
  colformat_double(j = c("db.orig.rev.pct.act", "db.final.rev.pct.act"), suffix = "%") %>% 
  bg(j = c("db.original.total.revenue", "db.orig.rev.error", "db.orig.rev.pct.act"), bg = mea_red_light, part = "all") %>%
  bg(j = c("db.final.total.revenue", "db.final.rev.error", "db.final.rev.pct.act"), bg = mea_blue_light, part = "all") %>%
  bg(j = "fid.r.total.audit", bg = mea_gray_light, part = "all") %>%
  flextable_custom_theme(title = "Table 4. Budgeted General Fund Revenue")

```



```{r}

FA_Data_District %>% 
  select(FY, db.orig.rev.pct.act, db.final.rev.pct.act) %>%
  pivot_longer(cols = c(db.orig.rev.pct.act, db.final.rev.pct.act)) %>%
  mutate(name = case_when(name == "db.orig.rev.pct.act"  ~ "Original",
                            name == "db.final.rev.pct.act" ~ "Final")) %>%
  ggplot(aes(x = FY, y = value, color = name, linetype = name)) +
  geom_line(size = line_size) +
  geom_hline(yintercept = 100) +
  scale_x_continuous(breaks = seq(1990, 2100, by = 1) )+
  scale_y_continuous(labels = number_format(suffix = "%")) +
  labs(title = "Figure 3. Original and Final Budgeted Revenue % of Actual",
       x = "Fiscal Year",
       y = "") +
  scale_color_manual(values = c(mea_blue, mea_red))+
  scale_linetype_manual(values=c(1, 2))+
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.box.background = element_rect(color= mea_gray, size=1))


```





### Budgeted Expenditure 

Table 5 and figure 4 compare General Fund expenditure expected in the district's original and final budgets to the actual expenditure spent in that fiscal year. 


```{r}
FA_Data_District %>% 
  filter(FY > (fiscal.year - prior.years.to.show),
         FY < fiscal.year
         ) %>% 
  select(FY, fid.r.total.audit ,
         db.original.total.expenditure, db.orig.exp.error, db.orig.exp.pct.act,
         db.final.total.expenditure, db.final.exp.error, db.final.exp.pct.act) %>% 
  flextable() %>%
  add_header_row(values = c("", "Original Budget", "Final Budget"),
                 colwidths = c(2,3,3)) %>% 
  set_header_labels(
                  FY = "Fiscal Year",
                  fid.r.total.audit = "Actual",
                  
                  db.original.total.expenditure = "Amount",
                  db.orig.exp.error = "Budget Error",
                  db.orig.exp.pct.act = "% of Actual ", 
                  
                  db.final.total.expenditure = "Amount",
                  db.final.exp.error = "Budget Error",
                  db.final.exp.pct.act = "% of Actual") %>% 
  colformat_double(big.mark = ",", digits = 0) %>%
  colformat_num(j = "FY", big.mark = "") %>% 
  colformat_double(j = c("db.orig.exp.pct.act", "db.final.exp.pct.act"), suffix = "%") %>% 

  bg(j = c("db.original.total.expenditure", "db.orig.exp.error", "db.orig.exp.pct.act"), bg = mea_red_light, part = "all") %>%
  bg(j = c("db.final.total.expenditure", "db.final.exp.error", "db.final.exp.pct.act"), bg = mea_blue_light, part = "all") %>%
  bg(j = "fid.r.total.audit", bg = mea_gray_light, part = "all") %>%
  flextable_custom_theme(title = "Table 5. Budgeted General Fund Expenditure")

```


```{r}

FA_Data_District %>% 
  select(FY, db.orig.exp.pct.act, db.final.exp.pct.act) %>%
  pivot_longer(cols = c(db.orig.exp.pct.act, db.final.exp.pct.act)) %>%
  mutate(name = case_when(name == "db.orig.exp.pct.act"  ~ "Original",
                            name == "db.final.exp.pct.act" ~ "Final")) %>%
  ggplot(aes(x = FY, y = value, color = name, linetype = name)) +
  geom_line(size = line_size) +
  geom_hline(yintercept = 100) +
  scale_x_continuous(breaks = seq(1990, 2100, by = 1) )+
  scale_y_continuous(labels = number_format(suffix = "%")) +
  labs(title = "Figure 4. Original and Final Budgeted Expenditure % of Actual",
       x = "Fiscal Year",
       y = "") +
  scale_color_manual(values = c(mea_blue, mea_red))+
  scale_linetype_manual(values=c(1, 2))+
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.box.background = element_rect(color= mea_gray, size=1))

```


